---
title: "Uber exercise"
author: "MM"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Uber exericise

Below is the exercise from StrataScratch easy section. Now I am just having fun working the MarkDown fancy file

## Downloading packages and reading the dataset:
```{r, echo=TRUE,results = "hide",message=FALSE,warning=FALSE}
library(tidyverse)
library(dplyr)
library(zoo)
x<-read.csv('Data/dataset_1.csv')
```
## Throwing a look
As we can see, weirdly  we have dates in a format as if we used the pivot table to create a dataset which will complicate our life later.
```{r, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
glimpse(x)
head(x,30)
```
## Data cleaning
Indeed, we will have to do some data cleaning to adjust the format such a way it is easier to work with the dates. We will need each observation have its own date.

First, I will do it my own artisanal way using loops I learnt at school
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
for (i in 2:nrow(x)) {  
  if (x$Date[i]=='') {  
    x$Date[i] <- x$Date[i - 1]  
  }
}
```
And as we can see, such an approach works very well
```{r, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
head(x,30)
```
Still, chatgpt offered me 2 other options :

**Step 1. Create a vector of T&F whether the cell is empty or not**
```{r, results = "hide", echo=FALSE,message=FALSE,warning=FALSE}
x<-read.csv('Data/dataset_1.csv')
```
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
x$Date==""
```
**Step 2. Take all the observations where the value is T and convert them in NA**
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
x$Date[x$Date == ""] <- NA
```
**Step 3. Fancy function to fill all the NA with the previous values a.k.a. forward filling**
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
x$Date <- na.locf(x$Date, na.rm = FALSE)
```
As a result, the same output
```{r, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
head(x,30)
```
# And Now we are good to do the exercise
## Exercise 1 : Which date had the most completed trips during the two week period?
Let's first check if the overall time period is 2-weeks:
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
min(x$Date)
max(x$Date)
```
Indeed, the period is 14 days as expected.
**Since we will potentially need working with grouped data let's create the dataset**
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
daily_rides<-x%>%
  group_by(Date)%>%
  summarise(
    completed_trips=sum(Completed.Trips,na.rm=TRUE),
    requests=sum(Requests,na.rm=TRUE),
    active_hours=n()
  )
# and select the date we need
filter(daily_rides,completed_trips==max(completed_trips))%>%
  select(Date,completed_trips)
```
Nice, now we know that there is been the most trips on 22nd September.
### However,  there is the smarter way to do that. 
And it is offered by **me** and suggest just executing one requests without creating any additional datasets
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
x%>%
  group_by(Date)%>%
  summarise(
    completed_trips=sum(Completed.Trips,na.rm=TRUE),
  )%>%
  filter(completed_trips==max(completed_trips))%>%
  select(Date,completed_trips)
```