---
title: "Uber exercise"
author: "MM"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Uber exericise

Below is the exercise from StrataScratch easy section. Now I am just having fun working the MarkDown fancy file

## Downloading packages and reading the dataset:
```{r, echo=TRUE,results = "hide",message=FALSE,warning=FALSE}
library(tidyverse)
library(dplyr)
library(zoo)
x<-read.csv('Data/dataset_1.csv')
```
## Throwing a look
As we can see, weirdly  we have dates in a format as if we used the pivot table to create a dataset which will complicate our life later.
```{r, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
glimpse(x)
head(x,30)
```
## Data cleaning
Indeed, we will have to do some data cleaning to adjust the format such a way it is easier to work with the dates. We will need each observation have its own date.

First, I will do it my own artisanal way using loops I learnt at school
```{r, eval=TRUE, echo=TRUE,message=FALSE,warning=FALSE}
for (i in 2:nrow(x)) {  
  if (x$Date[i]=='') {  
    x$Date[i] <- x$Date[i - 1]  
  }
}
```